\documentclass[main.tex]{subfiles}
\begin{document}



\section{Regulation and self-regulation in the crypto world}

Most of the DAOs deployed to blockchains such as Ethereum, Solana, and others are not supervised by any governments or laws. The smart contract will simply execute as specified by its programming. Rather than being supervised by formal processes and bodies, the DAOs are self-regulated by the entities deploying the smart contracts. Notably, they can decide to change the rules or update the smart contract of the DAOs by voting. Each DAO can function as a company, fund, or non-profit community. The token holders will vote and decide how to run the DAO. The DAO was invented by Christoph Jentzsch \cite{dao_paper}, the creator of The DAO concept and the author of the first DAO paper. Despite its initial divisiveness, the DAO concept is now very popular and widely used in the crypto world, leading to the Ethereum community split into the current "new" Ethereum and the original unforked "Ethereum Classic."

Though DAOs are self-regulated, they can still be regulated by governments, and many governments are trying to regulate the crypto world by providing legislation services for DAOs, regulating them under government and tax laws. This allows a DAO to run under the management of a registered company and engage in business activities such as providing services, making payments, and offering products. However, these regulated DAOs do not have the same level of freedom as fully self-regulated DAOs. Government-regulated DAOs are not built on top of a decentralized infrastructure, and governments can still regulate them through tax and stock market laws. While these regulated DAOs may not be as popular as self-regulated DAOs, governments are actively exploring various ways to regulate the crypto world.

Another way to run a DAO is without any legal entity, and most DAOs today operate in this fashion. All operations are proposed and voted on by the community token owners. The owners can buy tokens from decentralized exchanges (DEX) such as Uniswap and centralized exchanges (CEX) such as Coinbase, Binance, and FTX, and participate in the voting process to decide how to run the DAO. The core contributors and managers of these DAOs define the rules of the DAO in smart contracts, primarily using Solidity for Ethereum and Rust for Solana. They decide whether it's open source or private, define who can start a proposal, and set the voting rules such as proposal duration, voting approval threshold, and voting award with the minting of new tokens.

\subsection{Current designs of popular DAOs}

The design of DAOs has evolved over time, becoming more complex and incorporating additional features. As flaws, vulnerabilities, and inefficiencies were identified in older DAOs, current popular ones have emerged as resolutions to these issues. Some popular DAOs today include Aragon, Moloch, and DAOStack, among others.

One prominent feature among well-designed DAOs is the presence of a fully functional user interface for DAO governance. Efforts are made to reach out to individuals who are not familiar with blockchain coding or have limited coding knowledge, achieved through user-friendly interfaces. These DAOs require less technical expertise to participate without sacrificing any features for simplicity. Another common feature is the implementation of additional restrictions on a fundamental aspect of DAO governance: voting. For instance, Moloch adopts weighted voting instead of one vote per token, while Aragon utilizes a modular "court" as a dispute resolution mechanism to prevent 51\% attacks and malicious proposals. Most popular DAOs are also structured in a modular or compartmentalized manner, benefiting from enhanced organization and scalability, which are key focal points for many DAOs. Aragon, for example, incorporates various groups such as a group for all token holders, an executive sub-dao, a compliance sub-dao, and a tech group.

While these DAOs share several characteristics, they are differentiated by their unique key features. Moloch stands out in various aspects. Initially, it employed permissioned membership, allowing only existing members to vote on the addition of new members. Moloch also introduced a "ragequit" feature, enabling members to exchange all membership shares for treasury assets. Additionally, proposals required sponsorship before being eligible for voting, and a grace period was enforced for the execution of accepted proposals. Non-transferable power within the DAO is not necessarily a unique aspect. In Moloch v2, several new features were introduced, significantly shaping the current landscape of DAOs. These features include multi-class token support, allowing the use of up to 200 tokens instead of just one, funding proposals, open submissions for non-members, a "GuildKick" mechanism to remove malicious members, and more.

Another distinctive feature can be found in DAOStack, a popular DAO today. It incorporates ``holographic consensus,'' which addresses challenges arising from an overwhelming number of proposals and decision-making requirements. This approach enables a small group to vote on behalf of a larger majority, aligning with their desires. DAOStack also employs a separate metric called "reputation" instead of correlating tokens to voting power. This approach aims to prevent the emergence of a plutocracy, according to their belief.

Overall, DAOs are rapidly evolving, and their current designs vary significantly. There has been a notable shift in focus towards enhancing security and scalability. This shift stems from past and present instances of members losing their assets due to malicious actors exploiting non-restrictive and simplistic structures. Efforts are being made to enhance the security and robustness of voting, proposal submission, membership, and other aspects, alongside a strong emphasis on facilitating easy and efficient usage for all. However, as more DAOs emerge and investment in the DAO industry increases significantly, it becomes necessary for them to differentiate themselves from one another. As a result, we observe different features in Aragon, Moloch, and DAOStack, each attempting to address distinct challenges or create new tools. It is safe to say that there is still much room for improvement in DAOs, and we anticipate that future DAO designs will differ significantly from the present.


\subsection{``One token, one vote'' vs multi-class-token vote}

Most DAOs make decisions by creating proposals, submitting them to the community, and conducting community votes. Community members can vote by sending tokens to the DAO smart contract, which then counts the votes and determines the approval or rejection of the proposal. Each token represents one vote, and the majority of votes determines the outcome. However, the lack of regulations or restrictions on the ``majority'' of token owners in most DAOs can create significant safety and security risks. For example, if the co-founders hold 49.9\% of the total tokens and promise to sell the remaining 50.1\% to the community during project launch, they can regain control by purchasing 0.2\% of tokens anonymously. Without regulations beyond majority voting, the co-founders can mint new tokens or withdraw funds without limitations.

In comparison, modern corporations with stocks follow internal by-laws or public regulations regarding processes like ``follow-on public offerings (FPOs).'' Co-founders and major shareholders must disclose FPO information to the public, and FPOs are limited by the total number of shares. Government or regulatory agencies, such as the U.S. Securities and Exchange Commission, China Securities Regulatory Commission, or Hong Kong Securities and Futures Commission, regulate FPOs according to stock market laws. In private companies, co-founders and major shareholders can issue more shares through a process called "private placement," which is not regulated by stock market laws. However, they are still required to disclose information about the private placement to the public. Early-stage investors face strict restrictions on their shares, such as lock-up periods, vesting periods, and limits on the number of shares they can sell. Co-founders and major shareholders must also disclose information about these restrictions. Moreover, different shareholders and shares may have additional restrictions, such as non-dilution shares, anti-dilution shares, and super-voting shares, which must be disclosed to the public.

In modern stock corporations, while major issues require all-hands voting, daily operations are typically reviewed and approved by executives and the board of directors, rather than by a general vote from all shareholders. In contrast, many DAOs today solely rely on all-hands voting to approve community proposals, which can be inefficient and time-consuming. DAOs often set a voting threshold, such as 51\% of the votes, and a proposal is approved if the threshold is reached. They also establish a voting duration, such as one day, and a proposal is approved if the duration is met. Some DAOs offer a voting reward, such as 1\% of the total tokens, which is distributed to the majority voters. Additionally, to prevent excessive sequential proposals, DAOs usually set a minimum token ownership threshold for creating a proposal, for example, 10\%. Consequently, most token owners are not allowed to create proposals unless they meet the minimum token requirement. DAO proposal mechanisms can be designed as a blocking queue, where token owners must wait for the closure of previous proposals before creating new ones. This necessitates a multi-class hierarchy design for DAOs, enabling a multi-class-token voting system.

Another lesson from modern stock corporations is the concept of "super-voting shares." In joint-stock companies, super-voting shares have higher voting power than regular shares, providing owners with greater influence over decision-making processes within the company. Owners of super-voting shares may have more votes per share at shareholder meetings or the power to veto specific decisions. Companies often use super-voting shares to grant founders, executives, or key stakeholders more control over the company's direction. While this can align leadership with long-term interests, it may also create conflicts of interest and raise concerns about accountability and fairness.

The use of super-voting shares in corporate governance can be controversial, as it gives a small group of individuals disproportionate influence over the company. Consequently, laws and policies regulate the use of super-voting shares to balance the interests of different stakeholders. It is worth considering this concept as a potential way to design DAOs, although the use of super-voting shares should be approached carefully, taking into account corporate governance principles.

\subsection{By-laws and procedure}

The by-laws of a company consist of the rules and regulations that govern its internal operations and management. These by-laws cover various topics, including the organizational structure, officer and director responsibilities, meeting and voting procedures, and rules for share issuance and transfer.

Typically, the board of directors adopts the company's by-laws, which must then be approved by the shareholders. The purpose of these by-laws is to establish a clear and consistent framework for the company's governance and decision-making processes. They are regularly reviewed and updated to align with any operational or legal changes.

In some cases, external regulations from government agencies or industry bodies may also apply to a company's by-laws. For instance, publicly traded companies must ensure compliance with securities laws and other relevant regulations. Nonetheless, by-laws primarily serve as an internal document to ensure the company's smooth and effective operation.

In a self-regulated corporation, the by-laws focus on defining what actions are prohibited rather than what is permissible. They provide procedures for resolving potential issues that may arise in the future.

However, in the current design of DAOs, there is typically only one procedure: majority voting. Most DAOs only impose restrictions or regulations related to the voting process, such as voting thresholds, durations, awards, and minimum token requirements for proposal creation. However, there is no by-law that outlines prohibited actions or establishes procedures for addressing potential issues. As a result, major shareholders can easily control DAOs by proposing actions that harm minority shareholders, such as diluting their token holdings, or by executing "rug pull" proposals to drain funds from the DAOs. In this context, DAOs lack self-regulation through smart contract codes or community oversight. With decision-making solely dependent on majority voting, major shareholders can manipulate DAOs and create proposals that benefit themselves at the expense of others, leading to a "Tyrannical Majority" scenario.

In healthy, stable, and robust business entities like joint-stock companies or non-profit organizations, by-laws are crucial for defining what actions are prohibited and establishing procedures to address potential future problems. Shareholders, core executives, and the board of directors must set the boundaries of operations and rights within the organization before joining or investing. This enables them to prevent conflicts of interest and address potential problems. Similarly, in the design of DAOs, by-laws are essential to impose additional restrictions on different token owners before other token owners can purchase tokens from them. This approach goes beyond simple token voting, as relying solely on voting for all proposals cannot solve all problems and may even create further issues through the passage of "Tyrannical Majority" proposals.

\subsection{``Tokenomics'' vs ``Dividend''}

For DAOs and other crypto projects (SocialFi, GameFi, or other protocols), tokenomics is often used as a means to attract and retain investors, as compared to dividends. Tokenomics refers to the study of designing and implementing tokens within a cryptocurrency system. It involves creating a token, which is a digital asset used for exchange within a specific cryptocurrency ecosystem. Tokens represent value within the system, enabling the purchase and sale of goods and services, as well as incentivizing desired behaviors. The design of a token's economy is crucial for the overall success of a cryptocurrency, as it determines its utility and value over time. A well-designed token economy helps ensure the long-term viability and stability of the cryptocurrency.

This leads us to the question: are tokens in DAOs and crypto projects the same as stocks in traditional companies? Is purchasing or earning tokens equivalent to investing in stocks? Are token holders considered investors or customers? Are tokens comparable to stocks for investment purposes or products for sale?

In real-world companies regulated by the U.S. SEC, no company exists solely to sell ``stock'' to the market, and issuing 10 to 1000 times the stock without regulation is not feasible. There is a clear distinction between ``stock'' and ``product'': ``stock'' represents ownership in a company, encompassing not only ownership of assets and market value but also the right to participate in the company's decision-making process through specific procedures outlined in the company's by-laws, contracts, and regulations. Conversely, ``product'' refers to the goods or services produced and sold. It can encompass specific items offered for sale or the overall offering made to customers. In essence, companies generate revenue by creating goods or services as "products" for sale, while raising funds by issuing and selling new stock in primary or secondary markets, thereby diluting the ownership of existing shareholders. This mechanism forms the core of the traditional stock market, driving shareholders, executives, employees, and board members to collaborate and create tangible value while deriving profits from genuine business activities.

In most tokenomic designs, a precise definition of tokens is often lacking. Many DAOs and crypto projects utilize tokens to attract and retain investors, and these tokens can be traded on centralized (CEX) or decentralized (DEX) exchanges with voting power. However, tokens are not equivalent to stocks for investment purposes in most tokenomic designs. Firstly, in the majority of tokenomic algorithms, the core smart contract continually mints new tokens as rewards to SocialFi users, GameFi users, and DAO voters. This substantial increase in token supply leads to value dilution, reducing the significance and ownership weight of individual tokens. Secondly, smart contracts generally lack regulations or procedures guaranteeing the rights of token owners, apart from the "one-token one-vote" principle, which is often inefficient and time-consuming. It fails to prevent co-founders from executing rug pulls, in which they fraudulently withdraw assets belonging to other shareholders. Lastly, as observed in various cases, if co-founders can raise sufficient funds by minting and selling tokens through a ``tokenomics'' approach, they are likely to halt actual business expansion, allowing them to abscond with the funds (also known as a "rug pull") and abandon the project. Consequently, tokens are not equivalent to stocks for investment purposes, and the project's "business" revolves solely around "selling tokens" rather than creating and selling tangible goods or services. Consequently, token owners who purchase tokens for investment purposes differ from stock investors, despite believing in the illusion of a false ``tokenomics'' approach and anticipating token price appreciation with project growth, which typically yields opposite outcomes.

In a healthy and well-regulated stock market, most companies distribute dividends to their shareholders. Over 80\% of companies listed in the S\&P 500 index pay dividends periodically. Dividends hold significance for traditional stock companies as they allow companies to share their profits with shareholders. When a company generates a profit, it has various options for utilizing that money. It can reinvest the funds in the business to facilitate growth and expansion, pay off debts, or distribute a portion of the profits to shareholders in the form of dividends. Paying dividends helps companies attract and retain investors seeking regular income from their investments. Additionally, consistent dividend payments indicate financial stability and strength, enhancing investor confidence in the company. Some companies, particularly those in high-growth industries or prioritizing reinvestment of profits for fueling growth, may choose not to pay dividends.

Several reasons exist for companies opting not to pay dividends. Firstly, a company may lack surplus cash to distribute to shareholders. If a company is heavily investing in its operations, research and development, or other growth opportunities, it may not have available cash for dividend payments. In such cases, the company may retain profits to reinvest in the business and drive future growth.

Secondly, a company may believe that paying dividends is not the most effective way to generate value for its shareholders. For instance, a fast-growing company might believe that reinvesting profits in the business creates more value for shareholders than distributing dividends. In such cases, the company focuses on revenue and earnings growth, expecting this to result in higher share prices and better returns for shareholders.

Furthermore, some companies choose to forgo dividends to retain flexibility in capital allocation decisions. By retaining profits instead of paying dividends, companies can utilize their cash for acquisitions, strategic investments, or seizing other opportunities as they arise. This grants them greater control over their future and aids in building a stronger and more resilient business.

In conclusion, ``tokenomics'' is not the sole or appropriate approach for designing crypto projects or DAOs. Dividends offer a healthier and more stable method to stabilize token/stock prices in the market, as opposed to "infinitely minting tokens." However, dividends are not widely used in current crypto projects.

\section{Principles of DARC Protocol}

In designing DARC to be a regulated, programmable, customizable, profitable, and sustainable business entity, we adhere to the following principles:

\subsection{Plugin as a Law}

For real-world companies, compliance with a multitude of laws and regulations is essential. This compliance encompasses not only a company's By-laws but also its internal policies, agreements between the company and its employees, contracts with customers and suppliers, and agreements among shareholders. These agreements and rules define the operational procedures and boundaries of the company, forming the foundation for its healthy operation and growth. They not only determine the company's structure but also provide detailed descriptions of how the company operates and how profits are distributed.


As a purely virtual corporate entity existing solely on an EVM-compatible blockchain, within the DARC protocol, plugins serve as a core and foundational mechanism, representing a variety of by-laws, contracts, legal agreements, documents, and more. In each DARC protocol, there exists a set of plugins that form the fundamental laws governing the DARC. All operations and activities conducted within the DARC must rigorously adhere to and comply with all restrictions and conditions outlined by these plugins.

For the DARC protocol, plugins need to adhere to the following principles:

\subsubsection{Design of Plugins}

Each plugin consists of two crucial components: ``condition'' and ``decision''. The ``condition'' represents the triggering criteria that activate the plugin, while the ``decision'' specifies the actions to be taken when the condition is met. 
    
    The ``condition'' of each plugin is programmable and configurable, allowing for flexibility. When an operation is executed or when the DARC's state aligns with the specified condition, the plugin responds by implementing the corresponding "decision".

\subsubsection{Levels of Plugins}

For each operation, there is an associated ``level.'' Within each DARC protocol, there are multiple plugins, each of which may have the same or different levels. When multiple plugins are triggered simultaneously for a single operation, the DARC protocol selects the plugin with the highest level and uses that plugin's decision as the final decision.

Additionally, all plugins at the same level must have the same decision type. This requirement ensures that when multiple plugins at the same level are triggered simultaneously, the final decision is consistent. This design simplifies the decision-making process and ensures that there is no ambiguity when multiple plugins of the same level are involved.

\subsubsection{Immutability of Plugins}

Once a plugin is added to the DARC protocol, it cannot be changed or modified. Users have the capability to enable or disable one or multiple plugins through the use of ``enable operation'' or ``disable operation''.  When users wish to modify the rules represented by a plugin, they must disable the existing plugin that represents those rules and then add and enable a new plugin to replace it. This approach ensures that the integrity of the protocol is maintained while allowing for changes in the rules as needed by the users.

\subsubsection{Authority of Plugins}

In the DARC protocol, the plugin system holds authoritative control. For each operation, if it is rejected by the plugin system, it cannot proceed further. If the plugin system requires a vote, the operation can only be executed after undergoing the voting process. Only when the plugin system grants full approval can an operation be directly executed. This design ensures that the plugin system has the final say in the execution and validation of operations within the DARC protocol.

In the DARC Protocol, operations related to plugins include enabling plugins, disabling plugins, adding plugins, and adding and enabling a plugin. When users execute these actions associated with plugins, they are required to adhere to the regulations and constraints set by the existing plugins, just like any other operations. These operations targeted at plugins can only be executed after receiving approval from the current set of plugins.

In summary, any operations involving modifications to plugins must also receive approval from the current set of plugins. This ensures fairness and compliance with the rules and regulations established by the existing plugins within the DARC Protocol.


\subsection{Program and Operations}

For each DARC program, it consists of a series of operations, where each operation includes an opcode, a set of parameters, and an operator address. When an operator requests the DARC to execute a program, several scenarios may arise:

1. If one or more operations within this program receive a rejection decision from the plugin system, the entire program will be denied execution. In such a scenario, even if some of the operations meet the requirements, the program as a whole will be unable to proceed. 

2. If all operations within this program do not receive rejected decisions from the plugin system, but one or more operations in this program receive a ``voting needed'' decision, a voting process is initiated. In this scenario, all voting items will be consolidated into a single voting process, and the DARC enters a voting state. This allows all token holders to participate in the voting. If the program is approved through the voting process, it can proceed with execution. However, if it is rejected through the voting, the project will be rejected.

3. If each operation within this program receives an ``approved'' decision from the plugin system, in this scenario, all operations within the program can be executed sequentially and directly.

\subsection{Multi-level Token System}

The DARC protocol features a multi-level token system, with each level of tokens having independent voting weights and dividend weights, where the minimum values for these weights can be set to 0. It's important to note that the voting weight and dividend weights for each level of tokens are immutable and cannot be altered. Users have the capability to initialize a new level and perform a range of operations, including minting, burning, transferring, and more for all tokens.

By assigning voting weights and dividend weights to tokens at each level, imposing limitations on token quantities, and incorporating additional plugins to restrict and design various token-related operations, multi-level tokens can serve a multitude of purposes, including common stock, bonds, board votes, A/B shares, preferred stock, common commodities, Non-Fungible Tokens (NFTs), and more.

\subsection{Dividends}

A company has two methods of spending money: one is through direct cash payments, typically used for purchasing, salary disbursement, bill payments, and bond redemption, among other purposes. These payments generally involve one-time or multiple transactions of fixed amounts. The other method is through dividend payments, where the company allocates a specific amount or a certain percentage of funds and distributes them to all shareholders based on dividend weights.

In the DARC protocol, the dividend mechanism distributes a dividend, which consists of $X$ permyriad of the accumulated income from every $N$ transactions. This dividend is distributed to all token holders based on their dividend weight. 

In the DARC protocol, there is a dividend cycle counter. Every time the DARC receives a dividendable payment, this counter automatically increments by 1, and the amount of this payment is added to the dividendable fund pool. When the dividend cycle counter reaches the predefined dividend cycle $N$ within the DARC protocol, users can, subject to approval by the plugin system, execute the ``OFFER\_DIVIDENDS'' operation. This operation disburses $X$ permyriad of the funds from the dividendable fund pool, calculates the dividends, and distributes them to the accounts of each token holder. Subsequently, both the dividendable fund pool and the dividend cycle counter are reset to zero.

For the total amount $T$ in the dividendable fund pool and the sum of dividend weights of various token levels within the current DARC protocol, we can determine the dividend amount for each dividend unit as follows:

\[u = \frac{T}{W}\]

Here, $u$ represents the dividend amount for each dividend unit, $T$ is the total amount in the dividendable fund pool, and $W$ represents the sum of dividend weights for all dividendable tokens across different token levels within the current DARC protocol.

For each user, assuming that the sum of dividends from various token levels that user i holds is $D_i$, the total dividend amount $U_i$ that user i can receive in this round is given by:

\[ U_i = \frac{XD_i}{10000}u\]

For a sustainable and profit-generating DARC protocol, it is crucial to establish the correct values for $X$ and $N$. This is analogous to determining a stable and reasonable dividend yield in publicly traded companies. These values serve as a means to reward and incentivize token holders and also as a way to distribute profits to major stakeholders within the DARC protocol.

\subsection{Voting}

In the DARC protocol, for operations that cannot be directly approved or denied by the plugin system after triggering specific conditions, a voting mechanism can be employed to make the final decision. The voting mechanism can serve various purposes, including:

1. Democratic decision-making where all token holders have one vote each, suitable for major decisions involving a large number of token holders.

2. Quick and simple decision-making for smaller groups such as boards or committees.

3. Approval processes for routine tasks involving multiple managers taking turns to approve daily affairs.

4. Weighted voting processes for different groups, including A/B classes or multiple levels of voting rights.

For each plugin, if the decision is ``voting needed'', the plugin must be associated with a voting item. When the condition of this plugin is triggered, and the plugin has the highest level among all the plugins with triggered conditions, DARC will select the voting item specified by that plugin as the voting rule. Once all the voting items are collected by DARC, a voting process will be initiated based on these items. All token holders who meet the criteria specified by this series of voting items are eligible to participate in the voting.

After a program undergoes evaluation by the plugin system, each operation within the program may be subject to voting as requested by one or more plugins. Each plugin will point to a specific voting item. When DARC initiates a voting process, it collects all the voting items required for the operations and proceeds to the voting phase. Assuming that the total number of collected voting items is N, each voter must submit a program containing only one voting operation. This operation must include a boolean value array with a length of N, corresponding to the voting results for the N voting items. Each time an operator submits their vote, the voting process calculates the voting weight associated with that operator for each of the N voting items. It tallies the votes separately for each of the N voting items, adding the voting weight to the respective voting result. If a user's token balance is zero for one or more voting items, their voting weight for those specific items is also considered as zero.

\subsection{Emergency}

In a rule-based corporate virtual machine, DARC operators may encounter various types of errors, including operational errors, incorrect parameters in operations, and various potential non-technical conflicts and disputes. DARC maintains a backdoor, known as ``emergency agents'', to serve as firefighters in emergency situations.

In a DARC protocol, operators have the ability to designate multiple addresses as emergency agents. In the event of an emergency, and with the permission of the plugin system, operators can call upon one or more of these emergency agents for assistance. Once an emergency agent is summoned, they gain super-administrator privileges within the DARC, granting them the authority to perform any action. This includes adding, enabling, disabling plugins, conducting token operations, and managing cash assets.

Since emergency agents possess the highest level of comprehensive administrative authority, their role can be likened to that of both a court and a firefighter. Therefore, it is essential for all members of the DARC to have complete trust in these emergency agents. Additionally, specific conditions should be established for calling upon emergency agents to prevent them from taking untimely or inappropriate actions, which could lead to damage or losses within the DARC.

\end{document}