\documentclass[main.tex]{subfiles}
\begin{document}



\section{Principles of DARC Protocol}

In designing DARC to be a regulated, programmable, customizable, profitable, and sustainable business entity, we adhere to the following principles:

\subsection{Plugin as a Law}

For real-world companies, compliance with a multitude of laws and regulations is essential. This compliance encompasses not only a company's By-laws but also its internal policies, agreements between the company and its employees, contracts with customers and suppliers, and agreements among shareholders. These agreements and rules define the operational procedures and boundaries of the company, forming the foundation for its healthy operation and growth. They not only determine the company's structure but also provide detailed descriptions of how the company operates and how profits are distributed.


As a purely virtual corporate entity existing solely on an EVM-compatible blockchain, within the DARC protocol, plugins serve as a core and foundational mechanism, representing a variety of by-laws, contracts, legal agreements, documents, and more. In each DARC protocol, there exists a set of plugins that form the fundamental laws governing the DARC. All operations and activities conducted within the DARC must rigorously adhere to and comply with all restrictions and conditions outlined by these plugins.

For the DARC protocol, plugins need to adhere to the following principles:

\subsubsection{Design of Plugins}

Each plugin consists of two crucial components: ``condition'' and ``decision''. The ``condition'' represents the triggering criteria that activate the plugin, while the ``decision'' specifies the actions to be taken when the condition is met. 
    
The ``condition'' of each plugin is programmable and configurable, composed by a serial of condition expressions and logical operators(AND, OR, NOT). When an operation is executed with the condition triggered, the plugin responds by implementing the corresponding ``decision''. Below is an example of a plugin, designed in pseudo code:

\begin{spverbatim}

if ( 
    expressionA AND
    (expressionB OR expressionC) AND
    (NOT expressionD)
   ):
    decision = "approved"
    level = 100

\end{spverbatim}

The plugin condition above is a composed with four conditions, expressionA, expressionB, expressionC, expressionD, and three logical operators, AND, OR, NOT. When the condition is triggered, the plugin will make a decision of ``approved'' with a level of 100. In this way, each plugin can be designed to approve or deny operations based on the conditions and decisions specified by the plugin, and works as a law in the DARC protocol if the condition is triggered.

\subsubsection{Levels of Plugins}

For each operation, there is an associated ``level''. Within each DARC protocol, there are multiple plugins, each of which may have the same or different levels. When multiple plugins are triggered simultaneously for a single operation, the DARC protocol selects the plugin with the highest level and uses that plugin's decision as the final decision.

Additionally, all plugins at the same level must have the same decision type. This requirement ensures that when multiple plugins at the same level are triggered simultaneously, the final decision is consistent. This design simplifies the decision-making process and ensures that there is no ambiguity when multiple plugins of the same level are involved.

\subsubsection{Immutability of Plugins}

Once a plugin is added to the DARC protocol, it cannot be changed or modified. Users have the capability to enable or disable one or multiple plugins through the use of ``enable operation'' or ``disable operation''.  When users wish to modify the rules represented by a plugin, they must disable the existing plugin that represents those rules and then add and enable a new plugin to replace it. This approach ensures that the integrity of the protocol is maintained while allowing for changes in the rules as needed by the users.

\subsubsection{Authority of Plugins}

In the DARC protocol, the plugin system holds authoritative control. For each operation, if it is rejected by the plugin system, it cannot proceed further. If the plugin system requires a vote, the operation can only be executed after undergoing the voting process. Only when the plugin system grants full approval can an operation be directly executed. This design ensures that the plugin system has the final say in the execution and validation of operations within the DARC protocol.

In the DARC Protocol, operations related to plugins include enabling plugins, disabling plugins, adding plugins, and adding and enabling a plugin. When users execute these actions associated with plugins, they are required to adhere to the regulations and constraints set by the existing plugins, just like any other operations. These operations targeted at plugins can only be executed after receiving approval from the current set of plugins.

In summary, any operations involving modifications to plugins must also receive approval from the current set of plugins. This ensures fairness and compliance with the rules and regulations established by the existing plugins within the DARC Protocol.


\subsection{Program and Operations}

For each DARC program, it consists of a series of operations, where each operation includes an opcode, a set of parameters, and an operator address. Below is an example of a DARC program with four operations:

\begin{spverbatim}

// Notes: below is a DARC program with four operations
operation1(param1, param2);
operation2(param3);
operation3();
operation4(
    [value1, value2, value3], 
    [address1, address2, address3],
    param4
);

\end{spverbatim}

When an operator requests the DARC to execute a program, several scenarios may arise:

1. If one or more operations within this program receive a rejection decision from the plugin system, the entire program will be denied execution. In such a scenario, even if some of the operations meet the requirements, the program as a whole will be unable to proceed. 

2. If all operations within this program do not receive rejected decisions from the plugin system, but one or more operations in this program receive a ``voting needed'' decision, a voting process is initiated. In this scenario, all voting items will be consolidated into a single voting process, and the DARC enters a voting state. This allows all token holders to participate in the voting. If the program is approved through the voting process, it can proceed with execution. However, if it is rejected through the voting, the project will be rejected.

3. If each operation within this program receives an ``approved'' decision from the plugin system, in this scenario, all operations within the program can be executed sequentially and directly.

When the program is approved by the plugin system, the DARC will execute the program in the order in which the operations are listed. If the program is rejected by the plugin system, the DARC will not execute any of the operations within the program. The DARC may still throw exceptions if any runtime errors occur during the execution of the program. For example, if an operator attempts to transfer more tokens than it own, or disable a plugin with index larger than the total number of plugins, the DARC will throw an exception, reject the operation and the program, and revert the state of the DARC to the state before the program was executed.

\subsection{Multi-level Token System}

The DARC protocol features a multi-level token system, with each level of tokens having independent voting weights and dividend weights, where the minimum values for these weights can be set to 0. It's important to note that the voting weight and dividend weights for each level of tokens are immutable and cannot be altered. Users have the capability to initialize a new level and perform a range of operations, including minting, burning, transferring, and more for all tokens.

By assigning voting weights and dividend weights to tokens at each level, imposing limitations on token quantities, and incorporating additional plugins to restrict and design various token-related operations, multi-level tokens can serve a multitude of purposes, including common stock, bonds, board votes, A/B shares, preferred stock, common commodities, Non-Fungible Tokens (NFTs), and more.

Table \ref{table:6} is a simple example of a multi-level token system. In this example, the DARC protocol includes seven levels of tokens, each with different parameters and rules. The parameters include voting weight, dividend weight, and total supply. The rules include the conditions and decisions for minting, burning, transferring, and dividends. The table provides a comparison between the DARC protocol and a legal corporate entity, illustrating the similarities and differences between the two.

\begin{table}[h!]
    \centering
    \begin{tabular}{| c | c | c| c |} 
        \hline
        Level & Token Name & Parameters & Rules \\ [0.5ex] 
        \hline\hline
    0 & Board Member & \makecell[l]{Voting weight: 1 \\ Dividend weight: 0 \\ Total supply: 5} & \makecell[l]{1. Minting needs to be approved by \\  more than 70\% voting power of Class A \\ and B tokens. \\ 2. Burning or transferring needs to be \\ approved by all board members. \\ 3. Plugin-related operations need to \\ be approved by all board members.} \\
    \hline 
    1 & Executive  & \makecell[l]{Voting weight: 1 \\ Dividend weight: 0 \\ Total supply: 10} & \makecell[l]{1. Minting, burning or transferring needs \\ to be  approved by all board members. } \\
    \hline
    2 & Class A Stock & \makecell[l]{Voting weight: 1 \\ Dividend weight: 1 \\ Total supply: 1000000} & \makecell[l]{1. Minting needs to be approved by \\ all board members. \\ 2. Burning needs to be approved by \\ all board members. \\ 3. Transferring needs to be approved \\ by all board members if the owner of \\ tokens has more than 10\% of the total supply. \\ 4. DARC pays 20\% of the total income to all \\ Class A and B Stock owners as dividends.} \\
    \hline
    3 & Class B Stock & \makecell[l]{Voting weight: 10 \\ Dividend weight: 1 \\ Total supply: 500000} & \makecell[l]{1. Minting needs to be approved by \\ all board members. \\ 2. Burning needs to be approved by \\ all board members.} \\
    \hline
    4 & Corporate Bond & \makecell[l]{Voting weight: 0 \\ Dividend weight: 0 \\ Total supply: 1000000} & \makecell[l]{1. Minting 1 bond costs 10000 wei \\  before 2030-01-01. \\ 2. Burning 1 bond returns 13000 wei \\ after 2035-01-01 \\ and before 2031-02-01. \\ 3. Transferring 1 bond costs 100 wei. \\ 4. Total supply should be less than 1000000.} \\
    \hline 
    5 & Product Token & \makecell[l]{Voting weight: 0 \\ Dividend weight: 0 \\ Total supply: unlimited} & \makecell[l]{1. Minting 1 product token costs 2000 wei. \\ 2. Burning and refund needs to be  \\ approved by any executive.} \\
    \hline
    6 - 1000 & NFT & \makecell[l]{Voting weight: 0 \\ Dividend weight: 0 \\ Total supply: 1\\(for each level)} & \makecell[l]{1. Minting costs 10000000 wei per token. \\ 2. Burning is not allowed. \\ 3. Transferring costs 2500000 wei. \\ 4. If minting quantity is not 1, \\ or the supply of the target level is not 0, \\ minting is not allowed.} \\
    \hline
    \end{tabular}
    \caption{An example of a multi-level token system in the DARC protocol.}
    \label{table:6}
    \end{table}

\subsection{Dividends}

A company has two methods of spending money: one is through direct cash payments, typically used for purchasing, salary disbursement, bill payments, and bond redemption, among other purposes. These payments generally involve one-time or multiple transactions of fixed amounts. The other method is through dividend payments, where the company allocates a specific amount or a certain percentage of funds and distributes them to all shareholders based on dividend weights.

In the DARC protocol, the dividend mechanism distributes a dividend, which consists of $X$ permyriad of the accumulated income from every $N$ transactions. This dividend is distributed to all token holders based on their dividend weight. 

In the DARC protocol, there is a dividend cycle counter. Every time the DARC receives a dividendable payment, this counter automatically increments by 1, and the amount of this payment is added to the dividendable fund pool. When the dividend cycle counter reaches the predefined dividend cycle $N$ within the DARC protocol, users can, subject to approval by the plugin system, execute the ``\texttt{OFFER\_DIVIDENDS}'' operation. This operation disburses $X$ permyriad of the funds from the dividendable fund pool, calculates the dividends, and distributes them to the accounts of each token holder. Subsequently, both the dividendable fund pool and the dividend cycle counter are reset to zero.



\subsection{Voting}

In the DARC protocol, for operations that cannot be directly approved or denied by the plugin system after triggering specific conditions, a voting mechanism can be employed to make the final decision. The voting mechanism can serve various purposes, including:

1. Democratic decision-making where all token holders have one vote each, suitable for major decisions involving a large number of token holders.

2. Quick and simple decision-making for smaller groups such as boards or committees.

3. Approval processes for routine tasks involving multiple managers taking turns to approve daily affairs.

4. Weighted voting processes for different groups, including A/B classes or multiple levels of voting rights.

For each plugin, if the decision is ``voting needed'', the plugin must be associated with a voting item. When the condition of this plugin is triggered, and the plugin has the highest level among all the plugins with triggered conditions, DARC will select the voting item specified by that plugin as the voting rule. Once all the voting items are collected by DARC, a voting process will be initiated based on these items. All token holders who meet the criteria specified by this series of voting items are eligible to participate in the voting.

After a program undergoes evaluation by the plugin system, each operation within the program may be subject to voting as requested by one or more plugins. Each plugin will point to a specific voting item. When DARC initiates a voting process, it collects all the voting items required for the operations and proceeds to the voting phase. Assuming that the total number of collected voting items is N, each voter must submit a program containing only one voting operation. This operation must include a boolean value array with a length of N, corresponding to the voting results for the N voting items. Each time an operator submits their vote, the voting process calculates the voting weight associated with that operator for each of the N voting items. It tallies the votes separately for each of the N voting items, adding the voting weight to the respective voting result. If a user's token balance is zero for one or more voting items, their voting weight for those specific items is also considered as zero.

\subsection{Emergency}

In a rule-based corporate virtual machine, DARC operators may encounter various types of errors, including operational errors, incorrect parameters in operations, and various potential non-technical conflicts and disputes. DARC maintains a backdoor, known as ``emergency agents'', to serve as firefighters in emergency situations.

In a DARC protocol, operators have the ability to designate multiple addresses as emergency agents. In the event of an emergency, and with the permission of the plugin system, operators can call upon one or more of these emergency agents for assistance. Once an emergency agent is summoned, they gain super-administrator privileges within the DARC, granting them the authority to perform any action. This includes adding, enabling, disabling plugins, conducting token operations, and managing cash assets.

Since emergency agents possess the highest level of comprehensive administrative authority, their role can be likened to that of both a court and a firefighter. Therefore, it is essential for all members of the DARC to have complete trust in these emergency agents. Additionally, specific conditions should be established for calling upon emergency agents to prevent them from taking untimely or inappropriate actions, which could lead to damage or losses within the DARC.

\subsection{Compare DARC with Legal Corporate Entity}

Based on these principles, in Table \ref{table:4}, we compare the concepts of DARC and traditional joint-stock companies one by one. Although many concepts and mechanisms cannot be directly matched, this table attempts to analogize the similarities between DARC and traditional joint-stock companies, facilitating an understanding of various aspects of the DARC protocol.

Please note that due to DARC multi-token system, which can represent goods, different levels of equity, boards, committees, and other positions, and memberships can represent shareholders, special shareholders, employees, managers, and other operator roles and permissions, when using one or more levels of darc tokens or memberships to correspond to the characteristics and concepts of legal corporate entities, it is necessary to allow or prohibit operations based on the settings of the corresponding plugins. When a certain level of token or membership is endowed with a certain function or characteristic, and complete use of one or several plugins to specify the functions and rights of token holders and a certain level of membership, or to allow and prohibit operations, or to allow voting processes and scenarios, in such cases, these tokens and memberships can be used to represent these functions and characteristics.

\begin{table}[h!]
\centering
\begin{tabular}{| l | l | l|} 
    \hline
    Concept & DARC & Legal Corporate Entity \\ [0.5ex] 
    \hline\hline

    Currency & \makecell[l]{Native tokens of \\ EVM-compatible blockchain} & \makecell[l]{Fiat currency \\ (U.S. dollar, Euro, etc.)} \\
    \hline
    Corporate Entity & \makecell[l]{Compiled and deployed \\ DARC  virtual machine on \\  EVM-compatible blockchain} & \makecell[l]{Registered corporations \\ under government office} \\
    \hline
    Shares & \makecell[l]{DARC tokens \\ (with voting weight \(\ge\) 1 \\ and dividend weight \(\ge\) 1)} & Stock certificates \\
    \hline
    Shareholders & DARC token holder addresses & Shareholders \\
    \hline
    Capital Structure & \makecell[l]{DARC tokens \\ (with different voting weights \\ and dividend weights)} & \makecell[l]{Class A/B/C stocks, \\ preferred stocks } \\
    \hline
    Bonds & \makecell[l]{DARC tokens \\ (mintable at a certain price, \\ burnable at another certain price)} & Bond certificates \\
    \hline
    By-laws & A set of plugins & By-law documents \\
    \hline 
    Board of directors & \makecell[l]{DARC token holder addresses \\ (with limited supply) \\ and a set of plugins} & Human committee members  \\
    \hline
    Executives & \makecell[l]{Operator addresses \\ (with certain memberships) \\ and a set of plugins} & Human executives \\
    \hline
    Employees & \makecell[l]{Operator addresses \\ (with certain memberships) \\ and a set of plugins} & Human employees \\
    \hline
    \makecell[l]{Operation and \\Management} & \makecell[l]{Run By-law Script} & Sign documents \\
    \hline





    \hline
\end{tabular}
\caption{A comparison of the structures of DARC and a legal corporate entity}
\label{table:4}
\end{table}

For daily operations and management, we also compare various concepts of DARC and legal corporate entities in Table \ref{table:5}.

\begin{table}[h!]
    \centering
    \begin{tabular}{| l | l| l|} 
        \hline
        Concept & DARC & Legal Corporate Entity \\ [0.5ex] 
        \hline\hline
    By-laws & \makecell[l]{1. Design all the core plugins related to by-laws. \\ 2. Design and run a By-law Script program including:\\ 2.1 Add and enable all plugins to the DARC. \\ 2.2 Add emergency agents. \\ 2.3 Add profile information. } & Write and sign by-law documents \\
    \hline
    Issuing shares & \makecell[l]{Design and run a By-law Script program including: \\ 1. Initialize token classes and information. \\ 2. Mint common stock tokens to shareholders. \\ 3. Mint board member tokens to board member.} & \makecell[l]{Issue stock certificates} \\
    \hline
    Investment & \makecell[l]{1. Design and run a By-law Script program including: \\ 1.1 Mint common stock tokens to shareholders. \\ 1.2 Disable unnecessary previous stock-related plugins. \\ 1.3 Add and enable new agreement plugins. \\ 1.4 Pay certain amount of tokens. \\ 2. Vote and approve the program. \\ 3. Execute the approved program. } & \makecell[l]{Issue stock certificates} \\
    
    \hline
    Employment & \makecell[l]{Design and run a By-law Script program including: \\ 1. Add a new membership level, if necessary.\\ 2. Add new plugins to allow operator with \\ certain membership to withdraw cash monthly. \\ 3. Add new plugins to allow operator with \\ certain membership to mint RSU tokens annually. \\ 4. Add new employees to the membership. \\ 5. Allow manager-level operator to dismiss employee\\(removing employee from membership level).   } & \makecell[l]{Sign employment contracts, \\ pay payrolls and options/RSUs} \\
    \hline
    Purchase & \makecell[l]{Design and run a By-law Script program including: \\ 1. Pay cash to certain address \\ (External owned account, another DARC, \\ or other smart contract). }  & \makecell[l]{Electrical funds transfer \\ (eChecks, wire transfers, etc.)} \\
    \hline
    Dividends & \makecell[l]{Design and run a By-law Script program including: \\ 1. Offer dividends. } & \makecell[l]{Pay dividends quarterly or \\ yearly with payments} \\
    \hline 
    Stock tranding & \makecell[l]{Design and run a By-law Script program including: \\ 1. Transfer tokens from one address to another. } & \makecell[l]{Stock trading privately, \\ or on stock exchanges \\ or over-the-counter (OTC) \\ markets} \\
    \hline
    Accept payments & \makecell[l]{Send or transfer native tokens to DARC, \\ or withdraw native tokens from other DARCs \\ or smart contracts.} & \makecell[l]{Accept payments from customers, \\ suppliers, and other parties} \\
    \hline 
    Governance & \makecell[l]{Design and run a By-law Script program including: \\ 1. Design voting rules and add to the DARC. \\ 2. Add plugins to define scenarios that voting are needed. \\ Do voting when program is pending and voting is needed. } & \makecell[l]{Board meetings, \\ shareholder meetings, \\ and other corporate governance} \\
    \hline 
    \makecell[l]{Dispute and \\ litigation} & \makecell[l]{1. Add and enable emergency agents. \\ 2. Call emergency agents to resolve disputes. \\ 3. Contact emergency agents,  provide necessary \\ information, and pay the fee. \\ 4. The emergency agent operator takes over \\ the  DARC management, resolve issues or restore states.} & \makecell[l]{Legal actions, \\ arbitration, and mediation} \\
    \hline
    
    
    
        \hline
    \end{tabular}
    \caption{A comparision of operation and management between DARC and legal corporate entity}
    \label{table:5}
    \end{table}

\end{document}